---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# httc

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

httc makes it easy to quickly cache HTTP responses according to cache control headers with drop in wrappers for [httr](https://httr.r-lib.org/) verbs. For more control over caching behaviour, `caching()` lets you customize your own cached function.

## Installation

httc is not on CRAN. You can install the development version on GitHub with:

``` r
remotes::install_github("mikmart/httc")
```

## Example

Drop in a `httc::GET` instead of `httr::GET` to honour cache control headers:

```{r example}
# Response header specifies two seconds of caching
cached_request <- function() {
  try(httc::GET("https://httpbin.org/cache/2"))
}

system.time(cached_request()) # First response from server
system.time(cached_request()) # Second uses cached result
Sys.sleep(2)
system.time(cached_request()) # Re-requested from server
```
